Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-08-12 paperIEEE.tex
Final touches
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@144 db7c848b-7755-4df2-b763-8796797afa52

For sort-first and sort-last rendering we present static and load-balanced task
decomposition. For readability, we only present the results of the equalizer
(load or tree) providing the better performance for each application.
Unsurprisingly, static decompositions perform worse over load-balanced
compounds. Sort-first polygon rendering exhibits oscillations in performance as
nodes are added to the task, due to unfavorable assignment of a tile with a high
work load on odd node counts. Static sort-last volume rendering has a similar
oscillation behaviour, as ranges of scene geometry tend to also get unfavorably
assigned under such conditions. It seems plausible that this is also due to overheads associated with these two rendering scenarios. That is, volume rendering typically benefits less form sort-last decompositions, because of higher costs for compositing. Similarly, polygonal rendering often benefits less from sort-first decomposition, as compositing costs are typically much lower, while culling of geometry can create an additional overhead.

>>>>

For sort-first and sort-last rendering we present static and load-balanced task
decomposition. For readability, we only present the results of the equalizer
(load or tree) providing the better performance for each application.
Unsurprisingly, static decompositions perform worse over load-balanced
compounds. Sort-first polygon rendering exhibits oscillations in performance as
nodes are added to the task, due to unfavorable assignment of a tile with a
high work load on odd node counts. Static sort-last volume rendering has a
similar oscillation behaviour, as ranges of scene geometry tend to also get
unfavorably assigned under such conditions. For our polygonal rendering setup,
the amount of data exceeds the GPU memory, therefore sort-last rendering
exhibits a better scaling behaviour since it reduces the amount of geometry
data per GPU. For volume rendering, sort-first performs better since it has
less compositing overhead and is easy to load balance.
